Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow

### 2016-08-03 paper/widegap_mri_paper.tex
a little more intro for widegap

The magnetorotational instability (MRI) is thought to be a crucial driver of angular momentum transport and turbulence in astrophysical disks. (more MRI intro)

@@

>>>>

The magnetorotational instability (MRI) drives angular momentum transport and turbulence in astrophysical disks. Its discovery by \citeauthor{Balbus:1991vs} (\citeyear{Balbus:1991vs}; actually a rediscovery of \citei{Chandrasekhar:1960wh}) was a breakthrough in the longstanding question of how efficient accretion can exist in the universe: that is, how matter collapsing onto a central body is able to coalesce despite the conservation of specific angular momentum. %The ubiquity of disks ...

Magnetic fields were once assumed to have a stabilizing effect

@@

\bibitem[{Balbus \& Hawley(1991)}]{Balbus:1991vs}
Balbus, S A and Hawley, J F, 1991, The Astrophysical Journal, 376, 214

\bibitem[{Chandrasekhar(1960)}]{Chandrasekhar:1960wh}
Chandrasekhar, S. 1960, Proceedings of the National Academy of Sciences of the United States of America, 46, 253
